\documentclass[a5paper,8pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[T2A]{fontenc}
\usepackage{geometry}
\geometry{tmargin=2cm, bmargin=2cm, lmargin=1.7cm, rmargin=1.7cm}
\usepackage{float}
\usepackage{amsmath}
\usepackage{physics}
\usepackage{graphicx}
\usepackage[russian, english]{babel}

\pagestyle{myheadings}
\setcounter{page}{69}

\begin{document}

Horatio says 'tis but our fantasy,
And will not let belief take hold of him
Touching this dreaded sight, twice seen of us:
Therefore I have entreated him along
With us to watch the minutes of this night;
That if again this apparition come,
He may approve our eyes and speak to it.

\begin{equation}
    a = b + 4*c + 67*m*c^2
\end{equation}

Tush, tush, 'twill not appear.

$E = m*c^2$

BERNARDO
Sit down awhile;
And let us once again assail your ears,
That are so fortified against our story
What we have two nights seen.

$q = w * e - r * e ^ 2 + 1000$

the end

$
    x^2 + y^2 = z^2
$

$y = k*x + b$

\begin{equation}
    a + b + c < 0
\end{equation}

BERNARDO
Last night of all,
When yond same star that's westward from the pole
Had made his course to illume that part of heaven
Where now it burns, Marcellus and myself,
The bell then beating one,--
Enter Ghost

MARCELLUS
Peace, break thee off; look, where it comes again!

$ 
\phi = \omega*t - k*z
$

PRINCE FORTINBRAS
Let four captains
Bear Hamlet, like a soldier, to the stage;
For he was likely, had he been put on,
To have proved most royally: and, for his passage,
The soldiers' music and the rites of war
Speak loudly for him.
Take up the bodies: such a sight as this
Becomes the field, but here shows much amiss.
Go, bid the soldiers shoot.
A dead march. Exeunt, bearing off the dead bodies; after which a peal of ordnance is shot off
\end{document}